R Notebook for conducting Minimum Detectable Change (MDC) Analysis to design a monitoring strategy for the Upper Yaquina River TMDL Implementation Plan

### 2024-02-15 msc.Rmd
function works and returns the MDC for log10 y values. Need to trnsform the MDC for current model and MDC with additional samples to percent to compare

mdeol

MDC <- calculateMDCWithAdditionalSamples(model, additional_samples, alpha, power)
print(paste("MDC for", initial_n + additional_samples, "total samples:", MDC))

>>>>

df_cur <- df_log10 %>% filter(STATION == "12301") 
str(df_cur)

model_cur <- lm(log10_EC_val ~ date, df_cur)

MDC <- calculateMDCWithAdditionalSamples(model_cur, additional_samples = 36, 
                                         alpha = 0.05, power = 0.9)
print(paste("MDC for", initial_n + additional_samples, "total samples:", MDC))
